\thesistitle

### 2019-08-17 sections/discussion.tex
:)

>>>>

Regarding performance (Figure~\ref{fig:performance}, there is a notable difference between the refactoring-oriented clone types and the literature clone types. Type 1R-3R take about 6 times longer to detect than type 1-3. The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable- and method-references.

### 2019-08-17 sections/results.tex
:)

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/TypeResults}
    \caption{Number of cloned nodes.}
\label{fig:typeres}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/DurationChart}
    \caption{Duration in minutes of identifying clones for clone type definitions.}
  \label{fig:performance}
  \end{minipage}
\end{figure}

\begin{figure}[H]
  \centering
    \includegraphics[width=.5\columnwidth]{img/TypeResults}
      \caption{Number of cloned nodes.}
  \label{fig:typeres}
\end{figure}

\subsection{Performance}
We also measured the duration of finding clones by the different clone types. Figure~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types. The reason for this is further explained in Section~\ref{chap:challenge}.

\begin{figure}[H]
  \centering
    \includegraphics[width=.5\columnwidth]{img/DurationChart}
    \caption{Duration in minutes of identifying clones for clone type definitions.}
  \label{fig:performance}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{img/TypeResults}
    \caption{Number of cloned nodes.}
\label{fig:typeres}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{img/DurationChart}
    \caption{Clone type performance.}
  \label{fig:performance}
  \end{minipage}
\end{figure}

\subsection{Performance}
To map the viability of refactoring-oriented clone types for large scale clone detection, we measured the duration of finding clones by the different clone types. Figure~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. This figure shows the average duration of running CloneRefactor 10 times for a certain clone type. We ran these performance tests on the compute nodes of the DAS4 supercomputer \cite{bal2016medium}, which do not have many background processes severely affecting the results. The durations are of course dependent on our implementation of the clone types.
